\chapter{Conclusion and Future Work}
\label{chap5}
In the previous chapter, we have shown all the simulation and results of our proposed project. From introduction, Literature Review, Proposed Methodology, Result and Simulations. In this chapter, we will conclude our project and will 
\section{Conclusion}
This work describes the speech processing using MATLAB. We have:
\begin{enumerate}
\item Describe signals mathematically and understand
how to perform mathematical operations on signals.
%
\item This project provides knowledge of Digital filter
%
\item discuss word length issues ,multi rate signal processing and application
%
\end{enumerate}
In this project, we have record our speech of about 5 seconds at sampling frequency of 32 kHz.
we have use either ‘wavrecord()’ MATLAB function\\
After that we have:
\begin{enumerate}
\item Plotted the time and frequency domain magnitude spectrums of this speech signal.
 And found 327kHz is highest frequency of this signal and played that signal using
‘wavplay()’.
%
\item We have decimated the signal by a factor of 2 repeatedly. And again plotted the time and frequency domain
spectrum of the signal. And played the sound. Observation of this step is mentioned in detail in the Chapter \ref{chap4}.

%
\end{enumerate}

\section{Future Work}
Speech processing using MATLAB can be done in many other ways and the current method/project can be improve in many ways. Following are the some of the things we can try to improve this system:
\begin{enumerate}
\item Different method of the signal processing can be used to improve it.
%
\item High quality microphone can be used to improve the system accuracy.
%
%
\item Instead of using wavrecord, wavplay we can create the same project with the updated commands like audiorecorder/getaudiodata in MATLAB.
%
\item We can try on implementing the processing technique on multi subjects.
\end{enumerate}