\chapter{Literature Review}
\label{chap2}

In the chapter 1 we have given the introduction of our project, objectives and a thesis break down. Our introduction chapter is giving a complete overview of this project report. This chapter is about the work which is already been done on speech processing using MATLAB and will give a brief details about the articles, papers and literature review.

\section{Literature Review}
This chapter is about studies and literatures that are related to the Automatic Meter Reading that the proponents made use of different reading materials (such as thesis, articles, and other web articles) that will help extending the knowledge of the topic. These reading materials will also guide the proponent to improve and develop their proposed system more effectively.

Speech is one of the most important medium by which a communication can take place. With the invention and widespread use of mobiles, telephones, data storage devices etc. has provided a major help in setting up of speech communication and its analysing. The term and the basic concept of speech identification was began in the early 1960`s with exploration into voiceprint analysis which was somewhat similar to fingerprint concept. It was in 1984 that a science fiction called “Star Trek to George Orwell`s,” derived the concept that a machine can recognize the human voice.\cite{mandalia2011speaker}\\
Nowadays, with further growth \& advancement in the field of speech recognition, the humans who are physically challenged such as blind and deaf can easily communicate with the machines. So in biological terms a voice that is being generated through trachea will be decoded by brain.\cite{saxena2013speech}\\

The critical need for computationally efficient and user-friendly numerical software is hardly a matter of any controversy, although a number of key questions still remain wide open. In the current computing hardware landscape, any substantial gains in computational efficiency beyond the well-established best-practice techniques and standard software development tools (compilers, libraries, frameworks, etc.) usually come at the price of an increased customization for the target hardware. Such customizations tend to reduce the portability, readability, and maintainability of the code and frequently require specialized software development tools and skills to use them. The efforts to bridge the chasm between the readability/maintainability of numerical solver packages and the optimum performance on a given hardware are very active right now \cite{lawrence2018crossing} and generally aim to create higher abstraction levels for numerical software development such as domain specific languages (DSLs) paired with code generation capabilities.\cite{kuckuk2018whole},\cite{schulthess2015programming}




%\begin{table}[H]
%%\large
%\centering
%\caption{Consolidated Comparison of all the Systems}
%\label{tab2}
%%begin{adjustwidth}{-2.25in}{Oin}
%
%\begin{tabular}{|c|c|c|c|c|c|}
%\hline  %make a line
%Technology Used&Cost&Feasibility&Reliability&Communication Protocol\\
%\hline %make a line
%GSM&Low&Most Feasible&High&Stable\\
%\hline
%ZigBee&Medium&Small Scale&Low&Least Stable\\
%\hline
%SCADA&High&Not Feasible&High&Stable\\
%\hline
%PLC&Low&Least Feasible&Low&Very Stable\\
%\hline
%WiMAX&Medium&Small Scale&Medium&Stable\\
%\hline
%Mixed&Varies&Feasible&Varies&Varies\\
%\hline
%\end{tabular}
%\end{table}
%
%\small
%\begin{table}[H]
%\caption{Literature Review}
%\label{tab3}
%\centering
%\begin{tabularx}{1\linewidth}{X X X X}
%\toprule
% Paper Reference & Approach & Technology & Accuracy ($\%$) \\
%\toprule
%\cite{khan2020cost}&Cost Benefit Based Analytical Study of AMR and Blind Meter Reading (BMR) used by PESCO(WAPDA)& AMR and BMR &The Blind Meter Reading has internal financial return of about 84 percent while in case of AMR it is 15 percent.\\
%%\toprule
%\hline  %make a line
%\cite{zhao2005research} & Remote Meter Automatic Reading
%Based on Computer Vision & Computer vision techniques & $78\%$\\
%\hline %make a line
%\cite{li2019light} & Light-Weight Spliced Convolution Network-Based
%Automatic Water Meter Reading in Smart City & Network-Based
%Automatic Water Meter Reading & $85.66\%$ \\
%%\toprule
%\hline  %make a line
%\cite{dong2010design} & Wireless AMR System Based on SOPC & SOPC & $59.6\%$ \\
%\hline  %make a line
%\cite{ando2002automatic} & AMR system adopting automatic routing technology & routing technology & $68\%$ \\
%\hline  %make a line
%\cite{wiratama2018gas} & Gas
%billing system based on AMR on diaphragm gas meter with email
%notification & GSM or
%GPRS networks & $79\%$\\
%\hline  %make a line
%\cite{ashna2013gsm} & GSM based automatic AMR system with instant billing & GSM & $88\%$\\
%\hline  %make a line
%\cite{shuo2019digital} & Digital recognition of electric meter with deep learning & Deep Learning Methods & $78\%$\\
%\hline  %make a line
%\end{tabularx}
%\end{table}
%\small
%\begin{table}[H]
%\caption{-- continued from previous Literature Review table \ref{tab3}}
%\label{tab4}
%\centering
%\begin{tabularx}{1\linewidth}{X X X X}
%\toprule
% Paper Reference & Approach & Technology & Accuracy ($\%$) \\
%\toprule
%
%\cite{kulkarni2012gsm} &GSM based AMR system using ARM controller & ARM Controller & $81\%$\\
%\hline  %make a line
%\cite{Ali2012} & Implementation of (AMR) using radio frequency (RF) module & Radio Frequency & $58\%$\\
%\hline  %make a line
%\cite{palaniappan2015automated} & Comparison between different technologies being used in ARM  & GSM, Zigbee, SCADA System, Power Line Communication, WiMAX Technology,  & GSM = $88\%$, Zigbee = $67\%$,SCADA = $63\%$,Power Line = $71\%$,WiMAX = $62\%$,  \\
%\hline %make a line
%\cite{quan2010design} & Design of remote automatic meter reading system based on ZigBee and GPRS & ZigBee and GPRS techniques & $67\%$\\
%\hline  %make a line
%\cite{arun2012design} & Design and implementation of AMR system using GSM, ZIGBEE through GPRS & using GSM, ZIGBEE through GPRS & $89\%$\\
%\hline  %make a line
%\cite{rouf2012neighborhood} & Security and privacy analysis of automatic meter reading systems & Analysises of AMR & -\\
%\hline  %make a line
%\cite{malhotra2013automatic} & AMR and theft control system by using GSM & GSM & $84\%$\\
%\hline  %make a line
%\cite{tan2007automatic} & Automatic power meter reading system using GSM network & GSM network  & $78\%$\\
%\hline  %make a line
%\cite{Jamil2008} & Design and implementation of a wireless AMR system & GSM Network & $86\%$\\
%\hline  %make a line
%\cite{yuan2011remote} & Remote wireless AMR system based on GPRS & GPRS & $88\%$\\
%\hline  %make a line
%\cite{borle2013automatic} & AMR for electricity using power line communication & power line communication & $65\%$\\
%\hline  %make a line
%\end{tabularx}
%\end{table}
%\small
%\begin{table}[H]
%\caption{-- continued from previous Literature Review table \ref{tab4}}
%\label{tab5}
%\centering
%\begin{tabularx}{1\linewidth}{X X X X}
%\toprule
% Paper Reference & Approach & Technology & Accuracy ($\%$) \\
%\toprule
%\cite{mlakic2017designing} & Designing AMR system using open source hardware and software &open source hardware and software & $59\%$\\
%\hline  %make a line
%\cite{khalifa2010survey} & A survey of communication protocols for auto-
%matic meter reading applications, & Communication Protocols & - \\
%\hline
%\bottomrule
%\end{tabularx}
%\end{table}

\section{Concluding Remarks}
In this chapter, we have given a overall review about the literature related to Speech Processing Using MATLAB. MATLAB is a programming and numeric computing platform used by millions of engineers and scientists to analyze data, develop algorithms, and create models.\\\\
In the chapter 3 we will proposed methodology which we will use for our project with block diagrams, flowcharts, Mathematical Modeling, escudo code and component selection related to the hardware and software.

